---
title: 'Bayesian Structural Time Series: Weekly Box Office'
author: Dylan O'Connell
date: '2020-05-28'
slug: bsts-boxofice
categories: []
tags:
  - bayesian
  - R
subtitle: ''
summary: ''
authors: []
lastmod: '2020-05-28T13:54:36-04:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---




# Introduction

In this tutorial, I'll provide an introduction to the construction of Bayesian structural time series (BSTS) models, using Steve Scott's ![bsts package](https://cran.r-project.org/web/packages/bsts/bsts.pdf), applied to the total weekly box office gross (i.e. ticket sales) of American movie theaters. This is meant as a proof of concept and introduction (for myself, I'm making sure I understand the material), albeit geared at those already comfortable with statistics and R (I'll be explaining the parts unique to this application, but not any background). 

As we'll see, the class of models are likely not a particularly apt fit to the domain in question. This doesn't mean that there's no inferential value in the final result, but it does mean we have to be very conservative about what inferences we draw. BSTS models are exactly the sort of flexible structure that can provide alluringly useful accurate fits in certain contexts, only for the model to totally fall apart when stretched too far. This result is mostly due to my choice of data set (which I picked without careful consideration for its final use), but I think it's an illustrative example, because it can feel very natural to apply these models in ways which may not be theoretically sound (and they still might provide some insight in those cases, if used with appropriate caution). Above all, this is simply an opportunity for me to dip my toes into an unfamiliar topic, and I'm using this post as an excuse to articulate my own understanding of the topic, and make sure I'm comfortable with the basics.

# The Data

```{r, include = FALSE}
library(tidyverse)
library(bsts)
library(lubridate)
``` 

Our data is drawn from ![Box Office Mojo](https://www.boxofficemojo.com/weekly/), and it tallies the total dollar gross for each week of a given year. We will consider all weeks dating back to 1993.^[I.e. my lifetime.]

Box Office Mojo also tracks a few , like "Releases",^{The total number of distinct movies which grossed money that week.},"Top Release", and whether or not it is a long weekend. 

```{r, message = FALSE}
weekly.tb <- read_csv("weekly_gross.csv")
select <- dplyr::select
weekly.tb %>% names()
weekly.tb <- weekly.tb %>%
  as_tibble() %>%
  filter(year >= 1993) 
weekly.tb %>% head(3)
```

We will fit our model onto the log of the box office gross (using base 10, rather than the typical $e$, as this has a more intuitive numerical conversion for these large decimals). Intuitively, box office cannot be negative, so if we are fitting models which assume some sort of normality, this conversion is natural. Of course, we will see that while such a conversion fixes the most glaring violation of the assumptions, that does not automatically mean that the model fits! In fact, in this exploration we will see just how difficult it is to find a tidy model for box office gross.

```{r}
weekly.tb <- weekly.tb %>%
  mutate(time = year + (week-1)/52,
         log_gross = log10(gross),
         date = date_decimal(time)) %>%
  dplyr::select(date, time, gross, log_gross, releases, everything())
```

However, for the sake of clarity, we often will plot the model on the regular scale (without the log transformation), we simply note that below we fit the model to the logarithm of the gross as our response.
```{r}
weekly.tb %>%
  ggplot(aes(x = time, y = gross)) + 
  geom_line() + 
  xlab("Year") + 
  ylab("Gross ($)") + 
  ggtitle("Weekly (American) Box Office Gross") 
```


# Bayesian Structural Time Series Model
For this introduction, we will cite a Bayesian Structural Time Series (BSTS) model. We can take this piece by piece. A "Time Series" is a sequence of data points which are indexed by time. It's a particular category of statistics, because it fundamentally violates the core "independent and identically distributed" assumption that underpins much of statistical inference. While that renders many classical statistical procedures infeasible, the temporal relationship amongst the data is the whole point! We want to understand this evolution, which means that we must rely on a model which leverages this index on time. For notation, we write $y_1, \ldot, y_T$ for the response variables of interest (in this case, the log gross).

"Bayesian" follows its standard applied definition, as our objective is not a hypothesis test of point estimate with some desirable properties, but rather a posterior distribution on the parameters of interest (the parameters which describe our time series model). These parameters are determined by the "Structural" part of the model, whcih requires a careful definition. 

## The "Structural" Model

A "structural time series" is a model of response data indexed by time, whose temporal relationship is defined by the interplay of two equations. First, we have the *transition* equation, which models how a latent (i.e. unobserved state) $\alpha_t$ evolves over time. 
\begin{align}
\alpha_{t+1} &= T_t \alpha_t + R_t \eta_t, ~~~~~~ \eta_t &\sim N(0, Q_t)\label{eqn:bsts_transition}
\intertext{Before we explain any of these pieces, it's best to introduce the second part, the *observation* equation, which models how the observed response $y_t$ is generated using the state variable, $\alpha_t$.}
y_{t} &= Z_t^T \alpha_t + \epsilon_t, ~~~~~~ \epsilon_t &\sim N(0, H_t).\label{eqn:bsts_observation}
\end{align}
Thus, while a classic time series might model the relationship between $y_t$ and $y_{t+1}$ directly, a *structural* time series model instead links them through some latent, unobserved state, $\alpha_t$, which evolves underneath unseen, and influences the observed $y_t$ values. 

This is a sensible setup because often time series are understood to be random observations of some underlying "state" in our system, which we cannot observe directly. If you conduct monthly opinion polling with a relatively small sample, this can readily be understood as a structural time series, because the target of interest is the underlying latent state (the public's opinion on a particular issue), while the observations are noisy datum which are heavily influenced by that latent state. Thus, it makes sense for us to model our understanding of the latent state itself, rather than the latest noisy observation.^[Not classical time series don't have good ways of handling this problem too! While it would indeed be foolish to consider the prior observation, the sole piece of information denoting the current state, time series models have a rich array of tools to handle these complex forms of autocorrelation.]







The ![bsts package](https://cran.r-project.org/web/packages/bsts/bsts.pdf) is developed by Steve Scott, and provides a host of tools to make ABDDF. His specific approach, combining the Kalman filter with a spike-and-slab prior, was introduced in a ![neat paper](https://www.nber.org/chapters/c12995) showing how search trends could be used to "Nowcast".^[Forecasting an unobserved response occurring in the given moment]


Equation \ref{eqn:bsts_transition}.


# Sources

* The ![bsts package](https://cran.r-project.org/web/packages/bsts/bsts.pdf)
* ![Scott & Varian (2014)](https://www.nber.org/chapters/c12995)
* !["Fitting Bayesian structural time series with the bsts R package
, by Scott Varian, on the Google Unoficial Data Science Blog](http://www.unofficialgoogledatascience.com/2017/07/fitting-bayesian-structural-time-series.html)
* !["Sorry ARIMA, but I’m Going Bayesian
", by Kim Larsen](https://multithreaded.stitchfix.com/blog/2016/04/21/forget-arima/)




